A survey of HTTP caching options on the open Semantic Web

### 2015-01-19 sanity/paper1.tex
minor trim
git-svn-id: https://svn.ifi.uio.no/repos/users/kjekje-phd@1006 43ef1190-90fd-4dd7-a769-d0121f02b80e

\begin{table}
\caption{Recorded HTTP headers}\label{tab:headers}
 \begin{tabular}{ | l |  p{1.4cm} | p{6.8cm} |}
    \hline
    Header & Reference & Description \\ \hline
\httph{Age} & RFC7234 & When obtaining response from a cache, the number of
seconds since validation \\ \hline
\httph{Cache-Control} & RFC7234 & Header used for a variety of directives \\ \hline
\httph{Expires} & RFC7234  & Gives the date/time after which the
   response is considered stale. \\ \hline
\httph{Pragma} & RFC7234 & Archaic HTTP 1.0 header  \\ \hline
\httph{Warning} & RFC7234  & For additional information about possible incorrectness \\ \hline
\httph{Content-Type} & RFC7231 & To select the correct parser \\ \hline
\httph{If-None-Match} & RFC7232  & Request header to check if
                                   \httph{ETag} has changed   \\ \hline
\httph{If-Modified-Since} & RFC7232  & Request header to check if
                                   \httph{Last-Modified} has changed    \\ \hline
\httph{Last-Modified} & RFC7232 & When the resource was last modified \\ \hline
\httph{ETag} & RFC7232 & An opaque validator to check if the resource
has changed  \\ \hline
\httph{X-Cache} &  & Inserted by some caches to indicate cache status \\ \hline
\httph{Date} & RFC7231 & The time of the message. Used in conditional requests
and heuristics \\ \hline
\httph{Surrogates} & Edge \cite{edgearch} & Draft
to allow fine-grained control for proxies. \\ \hline
\httph{Client-Aborted} & libwww\footnote{https://metacpan.org/release/GAAS/libwww-perl-6.04}  & Header inserted by User
Agent to indicate that it aborted the download \\ \hline
\httph{Client-Warning} & libwww  & Header inserted by User
Agent to give details about problems with the download \\ \hline

@@

Based on the resulting headers, we first let libwww calculate the
freshness lifetime in seconds if it was possible, and recorded
that. Then, we also let it calculate a \emph{heuristic} freshness
time based on a suggestion in RFC7234, Section~4.2.2, and recorded that.

>>>>

\begin{table}
\caption{Recorded HTTP headers}\label{tab:headers}
 \begin{tabular}{ | l |  p{1.4cm} | p{6.8cm} |}
    \hline
    Header & Reference & Description \\ \hline
\httph{Age} & RFC7234 & When obtaining response from a cache, the number of
seconds since validation \\ \hline
\httph{Cache-Control} & RFC7234 & Header used for a variety of directives \\ \hline
\httph{Expires} & RFC7234  & Gives the date/time after which the
   response is considered stale. \\ \hline
\httph{Pragma} & RFC7234 & Archaic HTTP 1.0 header  \\ \hline
\httph{Warning} & RFC7234  & For additional information about possible incorrectness \\ \hline
\httph{Content-Type} & RFC7231 & To select the correct parser \\ \hline
\httph{If-None-Match} & RFC7232  & Request header to check if
                                   \httph{ETag} has changed   \\ \hline
\httph{If-Modified-Since} & RFC7232  & Request header to check if
                                   \httph{Last-Modified} has changed    \\ \hline
\httph{Last-Modified} & RFC7232 & When the resource was last modified \\ \hline
\httph{ETag} & RFC7232 & An opaque validator to check if the resource
has changed  \\ \hline
\httph{X-Cache} &  & Inserted by some caches to indicate cache status \\ \hline
\httph{Date} & RFC7231 & The time of the message. Used in conditional requests
and heuristics \\ \hline
\httph{Surrogates} & Edge \cite{edgearch} & Draft
to allow fine-grained control for proxies. \\ \hline
\httph{Client-Aborted} & libwww  & Header inserted by User
Agent to indicate that it aborted the download \\ \hline
\httph{Client-Warning} & libwww  & Header inserted by User
Agent to give details about problems with the download \\ \hline

@@

Based on the resulting headers, we let
libwww\footnote{https://metacpan.org/release/GAAS/libwww-perl-6.04}
calculate both standards-compliant and simple heuristic freshness
lifetime.
